---
title: "Calculate data statistics"
project:
  output-dir: outputs
date: last-modified
format: 
  html:
    page-layout: full
toc: true
editor: visual
warning: false
execute: 
  freeze: true
  warning: false
---

# Environment Setup

```{r setup}
# Packages
library(tidyverse)
library(tidyterra)
library(sf)

# Folder Structure
root <- rprojroot::has_file("extreme-heat-vs-sv.Rproj")$make_fix_file()
raw_data_dir <- root("data/raw")
proc_data_dir <- root("data/processed")
out_dir <- root("model_outputs")
```

# Notebook settings

```{r}
# Viz settings
col_palette <- c("#dc7726", "#eebb93", "#ecc046", "#f6e0a3", "#0292b7", "#81c9db", "#35A29F", "#97DECE")
```

# Functions

```{r}
source(file.path(src_dir, "model_check_utils.R"))
```

# Data Import

## Population

Data collected from: https://hub.worldpop.org/geodata/listing?id=139

### Lesotho

```{r}
lso_pop_files <- list.files(file.path(raw_data_dir, "population", "lso_2020"), full.names = TRUE)
rast_pops <- list()
for (i in seq_along(lso_pop_files)) {
  rast_pops[[i]] <- (
    terra::rast(lso_pop_files[i])
  )
}
popf_10_24_lso <- (
  sum(terra::rast(rast_pops))
  %>% rename(
    pop = sum
  )
)
```

### Mozambique

```{r}
moz_pop_files <- list.files(file.path(raw_data_dir, "population", "moz_2020"), full.names = TRUE)
rast_pops <- list()
for (i in seq_along(moz_pop_files)) {
  rast_pops[[i]] <- (
    terra::rast(moz_pop_files[i])
  )
}
popf_10_24_moz <- (
  sum(terra::rast(rast_pops))
  %>% rename(
    pop = sum
  )
)
```


### Namibia

```{r}
nam_pop_files <- list.files(file.path(raw_data_dir, "population", "nam_2020"), full.names = TRUE)
rast_pops <- list()
for (i in seq_along(nam_pop_files)) {
  rast_pops[[i]] <- (
    terra::rast(nam_pop_files[i])
  )
}
popf_10_24_nam <- (
  sum(terra::rast(rast_pops))
  %>% rename(
    pop = sum
  )
)
```

### Zambia

```{r}
zmb_pop_files <- list.files(file.path(raw_data_dir, "population", "zmb_2020"), full.names = TRUE)
rast_pops <- list()
for (i in seq_along(zmb_pop_files)) {
  rast_pops[[i]] <- (
    terra::rast(zmb_pop_files[i])
  )
}
popf_10_24_zmb <- (
  sum(terra::rast(rast_pops))
  %>% rename(
    pop = sum
  )
)
```

### Zimbabwe

```{r}
zwe_pop_files <- list.files(file.path(raw_data_dir, "population", "zwe_2020"), full.names = TRUE)
rast_pops <- list()
for (i in seq_along(zwe_pop_files)) {
  rast_pops[[i]] <- (
    terra::rast(zwe_pop_files[i])
  )
}
popf_10_24_zwe <- (
  sum(terra::rast(rast_pops))
  %>% rename(
    pop = sum
  )
)
```

## Temperature

```{r}
rast_temp <- terra::rast(
  file.path(
    raw_data_dir, 
    "temperature",
    "era5_t2m_max_2000-2020.nc"
  )
)
times <- terra::time(rast_temp)
```

## Model Data

```{r}
df_model_excess_hot_days_np_viol <- (
  read_csv(
    file.path(proc_data_dir, "df_model_excess_hot_days_np_viol.csv"),
    show_col_type = FALSE
  )
)
```

## Model

```{r}
fit_ranef_cou_excess_hot_days_np_viol <- readRDS(file.path(out_dir, "fit_ranef_cou_excess_hot_days_np_viol.rds"))
```


# Data Processing

## Total population by country

```{r}
tot_popf_10_24_lso <- (
  terra::global(
    popf_10_24_lso,
    fun = function(x) sum(x, na.rm = TRUE)
  )
)

tot_popf_10_24_nam <- (
  terra::global(
    popf_10_24_nam,
    fun = function(x) sum(x, na.rm = TRUE)
  )
)

tot_popf_10_24_moz <- (
  terra::global(
    popf_10_24_moz,
    fun = function(x) sum(x, na.rm = TRUE)
  )
)

tot_popf_10_24_zmb <- (
  terra::global(
    popf_10_24_zmb,
    fun = function(x) sum(x, na.rm = TRUE)
  )
)

tot_popf_10_24_zwe <- (
  terra::global(
    popf_10_24_zwe,
    fun = function(x) sum(x, na.rm = TRUE)
  )
)
```


## Affected Population

Resampling the population at the temperature grid.

```{r}
popf_10_24_lso_res <- exactextractr::exact_resample(
  popf_10_24_lso,
  rast_temp[[1]],
  "sum"
)
names(popf_10_24_lso_res) <- "pop_lso"

popf_10_24_moz_res <- exactextractr::exact_resample(
  popf_10_24_moz,
  rast_temp[[1]],
  "sum"
)
names(popf_10_24_moz_res) <- "pop_moz"

popf_10_24_nam_res <- exactextractr::exact_resample(
  popf_10_24_nam,
  rast_temp[[1]],
  "sum"
)
names(popf_10_24_nam_res) <- "pop_nam"

popf_10_24_zmb_res <- exactextractr::exact_resample(
  popf_10_24_zmb,
  rast_temp[[1]],
  "sum"
)
names(popf_10_24_zmb_res) <- "pop_zmb"

popf_10_24_zwe_res <- exactextractr::exact_resample(
  popf_10_24_zwe,
  rast_temp[[1]],
  "sum"
)
names(popf_10_24_zwe_res) <- "pop_zwe"
```

## Combine data

```{r}
df_rast_temp_pop <- (
  c(
    rast_temp, 
    popf_10_24_lso_res,
    popf_10_24_moz_res,
    popf_10_24_nam_res,
    popf_10_24_zmb_res,
    popf_10_24_zwe_res
  )
  %>% as_tibble()
  %>% mutate(
    tile_code = row_number()
  )
)
names(df_rast_temp_pop)[1: length(times)] <- as.character(times)
```


## Calculate historical statistics

```{r}
df_stats_hist <- (
  df_rast_temp_pop
  %>% mutate(
    country = case_when(
      pop_lso > 0 ~ "Lesotho",
      pop_moz > 0 ~ "Mozambique",
      pop_nam > 0 ~ "Namibia",
      pop_zmb > 0 ~ "Zambia",
      pop_zwe > 0 ~ "Zimbabwe"
    ),
    pop = rowSums(
      across(contains("pop")),
      na.rm = TRUE
    )
  )
  %>% select(
    -contains("pop_")
  )
  %>% filter(
    pop > 0
  )
  %>% pivot_longer(
    cols = -c("country", "tile_code", "pop"),
    names_to = "date",
    values_to = "temp"
  )
  %>% mutate(
    date = as.Date(date)
  )
  %>% group_by(country, tile_code)
  %>% mutate(
    hist_mean = mean(temp, na.rm = TRUE),
    hist_sd = sd(temp, na.rm = TRUE)
  )
  %>% ungroup()
  %>% mutate(
    sd_temp = (temp - hist_mean) / hist_sd,
    above_1sd = as.numeric(sd_temp > 1)
  )
  %>% select(-c(hist_mean, hist_sd, sd_temp))
)
```

## Calculate previous 12 month statistics

```{r}
df_stats_12m <- (
  df_stats_hist
  %>% arrange(country, tile_code, date)
  %>% group_by(country, tile_code, pop)
  %>% mutate(
    above_1sd_12m = slider::slide_index_dbl(
      .x = above_1sd,
      .i = date,
      .f = ~ sum(.x, na.rm = TRUE),
      .before = ~ .x %m-% months(12),
      .complete = TRUE
    )
  )
  %>% ungroup()
  %>% select(-c(above_1sd, temp))
  %>% filter(!is.na(above_1sd_12m))
  %>% group_by(country, tile_code, pop)
  %>% mutate(
    mean_days_above_1sd = mean(above_1sd_12m, na.rm = TRUE),
    sd_days_above_1sd = sd(above_1sd_12m, na.rm = TRUE)
  )
  %>% ungroup()
  %>% mutate(
    dev_days_above_1sd = if_else(
      sd_days_above_1sd == 0,
      0,
      (above_1sd_12m - mean_days_above_1sd) / sd_days_above_1sd
    )
  )
)
```

## Select time of reference

```{r}
df_stats_ref <- (
  df_stats_12m
  %>% filter(
    date == "2020-12-31"
  )
)
```

## Calculate population in exposure bins

```{r}
df_pop_affected <- (
  df_stats_ref
  %>% mutate(
    exp_bin = cut(
      dev_days_above_1sd, 
      breaks = c(-Inf, seq(1, 2, 1), Inf), 
      labels = c("pop_below_1", "pop_1_to_2", "pop_above_2"),
      include.lowest = FALSE
    )
  )
  %>% filter(
    dev_days_above_1sd > 1
  )
  %>% group_by(country, exp_bin)
  %>% summarise(
    pop = round(sum(pop, na.rm = TRUE)),
    .groups = "drop"
  )
  %>% ungroup()
  %>% pivot_wider(
    id_cols = country,
    names_from = exp_bin,
    values_from = pop,
    values_fill = 0
  )
)
```

```{r}
df_pop_affected
```

## Victimisation by country

```{r}
stats_vict <- generate_single_cont_marginal_by_group_df(
  fit_ranef_cou_excess_hot_days_np_viol, 
  df_model_excess_hot_days_np_viol, 
  cov = "heat", 
  grid_points = 15, 
  ndraws = min(brms::ndraws(fit_ranef_cou_excess_hot_days_np_viol), 1000), 
  group = "country"
)
```

```{r}
(
  stats_vict
  %>% filter(
    covariate_value >= -0.2
  )
  %>% mutate(
    heat = cut(
      covariate_value, 
      breaks = c(-0.2, 0.2, 1, 2, Inf),
      labels = c("baseline", "from_02_to_1", "from_1_to_2", "above_2")
    )
  )
  %>% group_by(group, heat)
  %>% summarise(
    median = median(median),
    .groups = "drop"
  )
  %>% pivot_wider(
    id_cols = group,
    names_from = heat,
    values_from = median
  )
  %>% mutate(
    excess_1_to_2 = from_1_to_2 - baseline,
    excess_2_plus = above_2 - baseline
  )
  %>% select(
    country = group,
    baseline,
    excess_1_to_2,
    excess_2_plus
  )
  %>% merge(
    df_pop_affected,
    by = "country",
    all.x = TRUE
  )
  %>% mutate(
    baseline_victims = round((pop_1_to_2 + pop_above_2) * baseline),
    excess_victims = round(pop_1_to_2 * excess_1_to_2 + pop_above_2 * excess_2_plus)
  )
  %>% select(
    country,
    baseline_victims,
    excess_victims
  )
)
```

