---
title: "Model temperature (number of excess hot days) effect on intimate partner sexual violence, all female"
format: html
editor: visual
---

# Environment Setup

```{r setup}
# Packages
library(tidyverse)
library(sf)
library(spdep)
library(brms)
options(brms.backend = "cmdstanr", mc.cores = 4)
library(cmdstanr)
library(posterior)
library(ggdist)
library(bayesplot)
library(tidybayes)
# theme_set(bayesplot::theme_default(base_family = "sans", base_size=14))
library(patchwork)
library(paletteer)
library(tidytext)
library(reliabilitydiag)

# Folder Structure
root <- rprojroot::has_file("agile2025.Rproj")$make_fix_file()
temp_dir <- root("temp")
dir.create(temp_dir, showWarnings = FALSE)
raw_data_dir <- root("data/raw")
model_data_dir <- root("data/processed/model_data")
fig_dir <- root("figures")
dir.create(fig_dir, showWarnings = FALSE)
mod_dir <- root("models")
src_dir <- root("src")

# Climate + violence data file
clim_fp_filename <- sort(list.files(model_data_dir, pattern = "climate_fp_\\d", full.names = TRUE), decreasing = TRUE)[[1]]
clim_fp_viol_filename <- sort(list.files(model_data_dir, pattern = "climate_fp_violence", full.names = TRUE), decreasing = TRUE)[[1]]
cat(paste0("Using data files:\n", clim_fp_filename, "\n", clim_fp_viol_filename))
```

# Notebook settings

```{r}
# Settings
nb_name <-  "Model effect of excess number of hot days on intimate partner sexual violence, all female"
seed <- sum(sapply(str_split(nb_name, pattern = "", simplify = TRUE), FUN = utf8ToInt))
set.seed(seed)

# Viz settings
col_palette <- c("#dc7726", "#eebb93", "#ecc046", "#f6e0a3", "#0292b7", "#81c9db", "#35A29F", "#97DECE")
label_map <- c(
  live_with_partner = "Live with partner (%)",
  school_level = "Education attainment (%)",
  rural = "Rural area (%)",
  over_18 = "Over 18 (%)",
  food_price_above_1sd_12m = "Months of food stress",
  clim = "Excess hot days (std.)",
  sv = "IP-SV victimisation (%)"
)

# Var settings
countries <- c("Lesotho", "Mozambique", "Namibia", "Zambia", "Zimbabwe")
clim_var <- "dev_value_temp_above_1sd_12m"
clim_label <- "excess_hot_days"
viol_var <- "sv_ip"
viol_label <- "ip_viol"
pop_label <- "all_female"
covars <- c(
  "sample_weight",
  "country",
  "adm_name",
  "cluster",
  "rural",
  "over_18",
  "school_level",
  "live_with_partner",
  "food_price_above_1sd_12m",
  viol_var
)
vars <- c(covars, clim_var)

bin_covs <- c(
  "rural",
  "over_18",
  "live_with_partner" 
)
mono_covs <- c(
  "food_price_above_1sd_12m",
  "school_level"
)
cont_covs <- c(
  "clim"
)

# Computation settings
adapt_delta = 0.95
iter = 2000
```

# Functions

```{r}
source(file.path(src_dir, "viz.R"))
source(file.path(src_dir, "model_check_utils.R"))

standardize <- function(x) {
  (x - mean(x)) / sd(x)
}
```

# Import Data

## Geometries

### Mozambique

```{r}
sf_moz <- (
  st_read(
    file.path(raw_data_dir, "geographies", "Mozambique 2022 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Zimbabwe

```{r}
sf_zwe <- (
  st_read(
    file.path(raw_data_dir, "geographies", "Zimbabwe 2015 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Lesotho

```{r}
sf_lso <- (
  st_read(
    file.path(raw_data_dir, "geographies", "Lesotho 2023 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Namibia

```{r}
sf_nam <- (
  st_read(
    file.path(raw_data_dir, "geographies", "Namibia 2013 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Zambia

```{r}
sf_zmb <- (
  st_read(
    file.path(raw_data_dir, "geographies", "Zambia 2018 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Create combined shapes

```{r}
sf_all <- (
  bind_rows(
    sf_moz,
    sf_zwe,
    sf_lso,
    sf_nam,
    sf_zmb,
  )
  %>% st_transform(3857)
  %>% mutate(
    centroid = st_centroid(geometry),
    lon = st_coordinates(centroid)[,1],
    lat = st_coordinates(centroid)[,2]
  )
)
```

## Climate & Food Prices

```{r}
df_clim <- (
  read_csv(
    clim_fp_filename,
    show_col_type = FALSE
  )
  %>% filter(
    country %in% countries
  )
)
```

## Survey Data

```{r}
df_clim_viol <- (
  read_csv(
    clim_fp_viol_filename,
    show_col_type = FALSE
  )
  %>% filter(
    !is.na(sample_weight),
    country %in% countries
  )
  %>% group_by(country)
  %>% mutate(
    country_sample_weight = sum(sample_weight, na.rm = TRUE)
  )
  %>% ungroup()
  %>% mutate(
    sample_weight = (
      1E-3 
      * sample_weight 
      * (
        sum(sample_weight, na.rm = TRUE) 
        / (length(unique(country)) * country_sample_weight)
      )
    ),
    over_18 = as.numeric(age > 18)
  )
)
```

```{r}
df_clim_viol_adm <- (
  df_clim_viol
  %>% group_by(country, adm_name)
  %>% summarise(
    clim = mean(!!sym(clim_var), na.rm = TRUE),
    rural = 100 * sum(rural * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    live_with_partner = 100 *sum(live_with_partner * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    over_18 = 100 * sum(over_18 * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    school_level = 100 * sum(school_level * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    food_price_above_1sd_12m = mean(food_price_above_1sd_12m, na.rm = TRUE),
    sv := 100 * sum(!!sym(viol_var) * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    .groups = "drop"
  )
  %>% merge(
    sf_all,
    by = c("country", "adm_name"),
    all.x = TRUE
  )
  %>% st_as_sf()
)
```

# Viz

## Covariate Maps

```{r}
#| fig-width: 10
#| fig-height: 10
p1 <- (
  ggplot(data = df_clim_viol_adm)
  + geom_sf(
    mapping = aes(fill = over_18),
    color = "transparent"
  )
  + scale_fill_distiller(
    palette = "Greys",
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14)
  )
  + labs(
    fill = "Over 18"
  )
)

p2 <- (
  ggplot(data = df_clim_viol_adm)
  + geom_sf(
    mapping = aes(fill = rural),
    color = "transparent"
  )
  + scale_fill_paletteer_c(
    palette = "ggthemes::Orange-Blue Diverging",
    direction = -1
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14)
  )
  + labs(
    fill = "Rural level"
  )
)

p3 <- (
  ggplot(data = df_clim_viol_adm)
  + geom_sf(
    mapping = aes(fill = live_with_partner),
    color = "transparent"
  )
  + scale_fill_distiller(
    palette = "Blues",
    direction = -1
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14)
  )
  + labs(
    fill = "Live with partner"
  )
)

p4 <- (
  ggplot(data = df_clim_viol_adm)
  + geom_sf(
    mapping = aes(fill = school_level),
    color = "transparent"
  )
  + scale_fill_distiller(
    palette = "Greens",
    direction = -1
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14)
  )
  + labs(
    fill = "School Attainment"
  )
)

p5 <- (
  ggplot(data = df_clim_viol_adm)
  + geom_sf(
    mapping = aes(fill = food_price_above_1sd_12m),
    color = "transparent"
  )
  + scale_fill_viridis_c(
    option = "viridis",
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14)
  )
  + labs(
    fill = "Food Stress Months"
  )
)

# layout <- "
#   ABE
#   CDE
# "
layout <- "
  ABC
  DEF
"

(
  (p1 + p2 + p3 + p4 + p5 + plot_spacer())
  + plot_layout(
    # widths = c(1, 1, 1.5),
    design = layout
  )
)
  
ggsave(
  path = fig_dir,
  filename = paste0("variable_comparison_", clim_label, "_", pop_label, "_", viol_label, ".png")
)
```

## Climate

### Distribution

```{r}
#| fig-width: 6
#| fig-height: 7
(
  ggplot()
  + geom_histogram(
    data = df_clim,
    mapping = aes(
      y = after_stat(ncount),
      x = !!sym(clim_var),
      fill = "clim"
    ),
    alpha = 0.7,
    bins = 20
  )
  + geom_histogram(
    data = df_clim_viol,
    mapping = aes(
      y = after_stat(ncount),
      x = !!sym(clim_var),
      fill = "clim_viol"
    ),
    alpha = 0.6,
    bins = 20
  )
  + geom_vline(
    xintercept = 0,
    color = "black",
    linetype = "dashed"
  )
  + facet_wrap(
    ~ country,
    ncol = 1
  )
  + scale_fill_manual(
    values = c(
      "clim" = col_palette[2],
      "clim_viol" = col_palette[5]
    ),
    labels = c(
      "clim" = "Climate variable distribution",
      "clim_viol" = "Climate at survey"
    )
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 13),
    strip.background = element_blank(),
    strip.text = element_text(size = 13),
    legend.background = element_blank(),
    legend.title = element_blank(),
    legend.text = element_text(size = 13),
  )
  + labs(
    y = "Counts (norm.)",
    x = "Excess hot days"
  )
)
```

```{r}
#| fig-width: 8
#| fig-height: 6
(
  ggplot()
  + geom_histogram(
    data = df_clim %>% filter(country == "Namibia"),
    mapping = aes(
      y = after_stat(ncount),
      x = !!sym(clim_var),
      fill = "clim"
    ),
    alpha = 0.7,
    bins = 20
  )
  + geom_histogram(
    data = df_clim_viol %>% filter(country == "Namibia"),
    mapping = aes(
      y = after_stat(ncount),
      x = !!sym(clim_var),
      fill = "clim_viol"
    ),
    alpha = 0.6,
    bins = 20
  )
  + geom_vline(
    xintercept = 0,
    color = "black",
    linetype = "dashed"
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 4
  )
  + scale_fill_manual(
    values = c(
      "clim" = col_palette[2],
      "clim_viol" = col_palette[5]
    ),
    labels = c(
      "clim" = "Climate variable distribution",
      "clim_viol" = "Climate at survey"
    )
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 13),
    strip.background = element_blank(),
    strip.text = element_text(size = 13),
    legend.background = element_blank(),
    legend.title = element_blank(),
    legend.text = element_text(size = 13),
    legend.position = "inside",
    legend.position.inside = c(0.5, 0.1)
  )
  + labs(
    y = "Counts (norm.)",
    x = "Excess hot days"
  )
)
```

### Map

```{r}
#| fig-width: 5
#| fig-height: 3

rng_clim <- range(df_clim_viol_adm$clim, na.rm = TRUE)

(
  df_clim_viol_adm
  %>% filter(country != "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = clim),
    color = "black",
    linewidth = 0.1
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "ggthemes::Orange-Blue Diverging",
    direction = -1,
    guide = guide_colorbar(
      label.position = "left",
      title.position = "right",
      title.vjust = 1,
      title.hjust = 0.5,
      barheight = unit(0.9, "npc")
    ),
    limits = rng_clim,
    rescaler = ~ scales::rescale_mid(., mid = 0),
    # oob = scales::squish
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    plot.margin = margin(r = 15),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(1.07, 0.5),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14, angle = 90),
    legend.ticks = element_line(color = "black")
  )
  + labs(
    fill = "Excess hot days (std.)"
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("map_heat_", clim_label, "_", pop_label, "_", viol_label, ".svg")
)
```

```{r}
#| fig-width: 4
#| fig-height: 2.5

rng_clim <- range(df_clim_viol_adm$clim, na.rm = TRUE)

(
  df_clim_viol_adm
  %>% filter(country == "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = clim),
    color = "black",
    linewidth = 0.2
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "ggthemes::Orange-Blue Diverging",
    direction = -1,
    limits = rng_clim,
    rescaler = ~ scales::rescale_mid(., mid = 0),
    # oob = scales::squish
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = NA, color = "black", linewidth = 3),
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )
  + guides(
    fill = "none"
  )
  + labs(
    fill = "Excess hot days (std.)"
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("map_heat_", clim_label, "_", pop_label, "_", viol_label, "_LSO.svg"),
  bg = "transparent"
)
```

## Violence

```{r}
#| fig-width: 5
#| fig-height: 3

rng_sv <- range(df_clim_viol_adm$sv, na.rm = TRUE)

(
  df_clim_viol_adm
  %>% filter(country != "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = sv),
    color = "black",
    linewidth = 0.1
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "grDevices::Rocket",
    direction = -1,
    guide = guide_colorbar(
      label.position = "left",
      title.position = "right",
      title.vjust = 1,
      title.hjust = 0.5,
      barheight = unit(0.9, "npc")
    ),
    limits = rng_sv,
    breaks = c(0, 5, 10)
    # rescaler = ~ scales::rescale_mid(., mid = 0),
    # oob = scales::squish
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    plot.margin = margin(r = 25),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(1.07, 0.5),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14, angle = 90),
    legend.ticks = element_line(color = "black")
  )
  + labs(
    fill = label_map[["sv"]]
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("map_sv_", clim_label, "_", pop_label, "_", viol_label, ".svg")
)
```

```{r}
#| fig-width: 4
#| fig-height: 2.5

rng_sv <- range(df_clim_viol_adm$sv, na.rm = TRUE)

(
  df_clim_viol_adm
  %>% filter(country == "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = sv),
    color = "black",
    linewidth = 0.2
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "grDevices::Rocket",
    direction = -1,
    limits = rng_sv
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = NA, color = "black", linewidth = 3),
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )
  + guides(
    fill = "none"
  )
  + labs(
    fill = "Mean SV victimisation"
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("map_sv_", clim_label, "_", pop_label, "_", viol_label, "_LSO.svg"),
  bg = "transparent"
)
```

# Prepare Data

## Restrict locations

```{r}
sf_vacs <- (
  sf_all
  %>% filter(
    country %in% (df_clim_viol$country %>% unique()),
    adm_name %in% (df_clim_viol$adm_name %>% unique())
  )
)
```

## Extract model subsets

```{r}
df_model <- (
  df_clim_viol
  %>% filter(
    female == 1,
    # age > 14
  )
  %>% select(all_of(vars))
  %>% na.omit()
  %>% merge(
    sf_vacs %>% as.data.frame() %>% select(country, adm_name),
    by = c("country", "adm_name"),
    all.x = TRUE
  )
  %>% mutate(
    country = factor(country),
    adm_name = factor(adm_name),
    cluster = factor(cluster),
    school_level = factor(
      school_level,
      levels = sort(unique(school_level)),
      ordered = TRUE
    ),
    food_price_above_1sd_12m = factor(
      food_price_above_1sd_12m,
      levels = sort(unique(food_price_above_1sd_12m)),
      ordered = TRUE
    ),
    clim := scale(!!sym(clim_var))
  )
)
```

## Generate adjacency matrix

```{r}
nb_list <- poly2nb(sf_vacs)
W <- nb2mat(nb_list, style = "B", zero.policy = TRUE)
rownames(W) <- sf_vacs$adm_name
colnames(W) <- sf_vacs$adm_name
levs <- levels(df_model$adm_name)
W_ord <- W[levs, levs]
```

```{r}
edges <- (
  geostan::edges(W, unique_pairs_only = TRUE, shape = sf_vacs$geometry)
)
graph <- st_geometry(edges)
```

```{r}
plot(sf_vacs$geometry, lwd = .15)
plot(graph, add = TRUE, type = "p", col = "red")
plot(graph, add = TRUE, type = "l", col = "black")
```

## Spatial correlation in raw data

```{r}
#| fig-width: 3
#| fig-height: 3
plot_moran(df_model, sf_vacs, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_obs_main_effect_", clim_label, "_", pop_label, "_", viol_label, ".png")
)
```

# Modeling

## Random Intercepts by admin level and cluster

```{r}
pars_ranint_adm_clu <- c(
  "b_Intercept",
  "b_countryMozambique",
  "b_countryNamibia",
  "b_countryZambia",
  "b_countryZimbabwe",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  "sd_adm_name__Intercept",
  "sd_adm_name:cluster__Intercept",
  "b_clim"
)
```

```{r}
stanvars <- stanvar(6, "num_pred")

prior_list_ranint_adm_clu <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_ranint_adm_clu <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + clim
        + (1 | adm_name/cluster)
      )"
    )
  )
)
fit_ranint_adm_clu <- brm(
  formula = form_ranint_adm_clu,
  family = bernoulli("logit"),
  prior = prior_list_ranint_adm_clu,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
sp <- rstan::get_sampler_params(fit_ranint_adm_clu$fit, inc_warmup = FALSE)
ebfmi_per_chain <- sapply(sp, function(chain_mat) {
  ener <- chain_mat[,"energy__"]
  mean(diff(ener)^2) / var(ener)
})
print(ebfmi_per_chain)
```

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_ranint_adm_clu), 
  pars = c(
    "b_Intercept", 
    "sd_adm_name__Intercept", 
    "sd_adm_name:cluster__Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_clim"
  ),
  np = nuts_params(fit_ranint_adm_clu),
  np_style = pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_ranint_adm_clu, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_ranint_adm_clu, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_ranint_adm_clu)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_ranint_adm_clu,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_ranint_adm_clu <- (
  fit_ranint_adm_clu
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_ranint_adm_clu,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_ranint_adm_clu <- (
  fit_ranint_adm_clu
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_ranint_adm_clu_stats <- (
  df_base_sv_by_country_ranint_adm_clu
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_ranint_adm_clu,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Climate Marginal Effects

##### Population level

```{r}
cont_marg_ranint_adm_clu <- generate_cont_marginal_df(fit_ranint_adm_clu, df_model, covs = c("clim"))
```

```{r}
#| fig-width: 4
#| fig-height: 3.5
(
  plot_continuous_marginal(fit_ranint_adm_clu, df_model, covs = c("clim"))
  + scale_y_continuous(
    # limits = c(0, 0.43),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranint_adm_clu.png")
)
```

#### Climate Variable Posterior

```{r}
df_clim_pop_adm_clu <- (
  fit_ranint_adm_clu
  %>% as.data.frame()
  %>% mutate(clim_pop = exp(b_clim))
  %>% summarise(
    median_val = median(clim_pop),
    # mean_val = mean(clim_pop),
    lower1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 1.2

lims <- c(
  min(df_clim_pop_adm_clu$lower2_val, 0.95), 
  max(df_clim_pop_adm_clu$upper2_val)
)

p1 <- (
  df_clim_pop_adm_clu
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p1

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_", clim_label, "_", pop_label, "_", viol_label, "_adm_clu.png")
)
```

### Calibration Checks

```{r}
#| fig-width: 4
#| fig-height: 3
plot_calibration(fit_ranint_adm_clu, df_model, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("calibration_plot_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranint_adm_clu.png")
)
```

### Residuals Spatial Correlation Checks

```{r}
#| fig-width: 3.2
#| fig-height: 3
plot_moran(df_model, sf_vacs, fit = fit_ranint_adm_clu, residuals = TRUE)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_res_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranint_adm_clu.png")
)
```

### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_ranint_adm_clu, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranint_adm_clu.png")
)
```

## Random Intercepts by admin level and cluster + Fixed interaction: country \* climate

```{r}
pars_fix_int_cc <- c(
  "b_Intercept",
  "b_countryMozambique",
  "b_countryNamibia",
  "b_countryZambia",
  "b_countryZimbabwe",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  "sd_adm_name__Intercept",
  "sd_adm_name:cluster__Intercept",
  "b_clim",
  "b_countryMozambique:clim",
  "b_countryNamibia:clim",
  "b_countryZambia:clim",
  "b_countryZimbabwe:clim"
)
```

```{r}
stanvars <- stanvar(6, "num_pred")

prior_list_fix_int_cc <- c(
  prior(student_t(3, -2, 1), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_fix_int_cc <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + (1 | adm_name/cluster)
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + country * clim
      )"
    )
  )
)
fit_fix_int_cc <- brm(
  formula = form_fix_int_cc,
  family = bernoulli("logit"),
  prior = prior_list_fix_int_cc,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
sp <- rstan::get_sampler_params(fit_fix_int_cc$fit, inc_warmup = FALSE)
ebfmi_per_chain <- sapply(sp, function(chain_mat) {
  ener <- chain_mat[,"energy__"]
  mean(diff(ener)^2) / var(ener)
})
print(ebfmi_per_chain)
```

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_fix_int_cc), 
  pars = c(
    "b_Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_clim",
    "sd_adm_name__Intercept",
    "sd_adm_name:cluster__Intercept"
  ),
  np = nuts_params(fit_fix_int_cc),
  np_style = pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_fix_int_cc, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_fix_int_cc, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_fix_int_cc)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_fix_int_cc,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_fix_int_cc <- (
  fit_fix_int_cc
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_fix_int_cc,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_fix_int_cc <- (
  fit_fix_int_cc
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_fix_int_cc_stats <- (
  df_base_sv_by_country_fix_int_cc
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_fix_int_cc,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Climate Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(fit_fix_int_cc, df_model, covs = c("clim"))
  + scale_y_continuous(
    # limits = c(0, 0.43),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.png")
)
```

##### By Country

```{r}
#| fig-width: 12
#| fig-height: 3
(
  plot_single_continuous_marginal_by_group(fit_fix_int_cc, df_model, cov = "clim")
  + scale_y_continuous(
    # limits = c(0, 0.35),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_by_country_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.png")
)
```

#### Climate Variable Posterior

```{r}
df_clim_fix_int_cc <- (
  fit_fix_int_cc
  %>% as.data.frame()
  %>% mutate(
    `b_countryLesotho:clim` = 0
  )
  %>% select(
    clim_pop = b_clim,
    contains(":clim")
  )
  %>% mutate(
    across(
      .cols = -clim_pop, 
      .fns = ~ exp((.) + clim_pop),
      .names = "{.col}"
    ),
    clim_pop = exp(clim_pop)
  )
  %>% rename(
    Overall = clim_pop,
  )
  %>% rename_with(
    .cols = -Overall,
    .fn = ~ str_match(., "b_country(.*?):clim")[,2]
  )
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    # mean_val = mean(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 3

lims <- c(
  min(df_clim_fix_int_cc$lower2_val, 0.9), 
  max(df_clim_fix_int_cc$upper2_val)
)

p1 <- (
  df_clim_fix_int_cc
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_clim_fix_int_cc
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.svg")
)
```

### Calibration Checks

```{r}
#| fig-width: 4
#| fig-height: 3
plot_calibration(fit_fix_int_cc, df_model, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("calibration_plot_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.png")
)
```

### Residuals Spatial Correlation Checks

```{r}
#| fig-width: 3.2
#| fig-height: 3
plot_moran(df_model, sf_vacs, fit = fit_fix_int_cc, residuals = TRUE)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_res_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.png")
)
```

### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_fix_int_cc, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fix_int_cc.png")
)
```

## Random slope by country

```{r}
pars_ranef_cou <- c(
  "b_Intercept",
  "b_countryMozambique",
  "b_countryNamibia",
  "b_countryZambia",
  "b_countryZimbabwe",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  "sd_adm_name__Intercept",
  "sd_adm_name:cluster__Intercept",
  "b_clim",
  "r_country[Lesotho,clim]"
)
```

```{r}
stanvars <- stanvar(6, "num_pred")

prior_list_ranef_cou <- c(
  prior(student_t(3, -2, 1), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_ranef_cou <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + (1 | adm_name/cluster)
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + clim
        + (-1 + clim | country)
      )"
    )
  )
)
fit_ranef_cou <- brm(
  formula = form_ranef_cou,
  family = bernoulli("logit"),
  prior = prior_list_ranef_cou,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = iter,
  control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
sp <- rstan::get_sampler_params(fit_ranef_cou$fit, inc_warmup = FALSE)
ebfmi_per_chain <- sapply(sp, function(chain_mat) {
  ener <- chain_mat[,"energy__"]
  mean(diff(ener)^2) / var(ener)
})
print(ebfmi_per_chain)
```

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_ranef_cou), 
  pars = c(
    "b_Intercept", 
    # "sd_adm_name__Intercept", 
    # "sd_adm_name:cluster__Intercept", 
    "r_country[Lesotho,clim]",
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_clim"
  ),
  np = nuts_params(fit_ranef_cou),
  np_style = pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_ranef_cou, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_ranef_cou, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_ranef_cou)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_ranef_cou,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_ranef_cou <- (
  fit_ranef_cou
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_ranef_cou,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_ranef_cou <- (
  fit_ranef_cou
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_ranef_cou_stats <- (
  df_base_sv_by_country_ranef_cou
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_ranef_cou,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Climate Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(fit_ranef_cou, df_model, covs = c("clim"))
  + scale_y_continuous(
    # limits = c(0, 0.43),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

##### By Country

```{r}
#| fig-width: 12
#| fig-height: 3
(
  plot_single_continuous_marginal_by_group(fit_ranef_cou, df_model, cov = "clim")
  + scale_y_continuous(
    # limits = c(0, 0.35),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_by_country_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

#### Climate Variable Posterior

```{r}
df_clim_pop_ranef_cou <- (
  fit_ranef_cou
  %>% as.data.frame()
  %>% select(clim_pop = b_clim)
)
df_clim_gr_ranef_cou <- (
  as_tibble(ranef(fit_ranef_cou, summary = FALSE)$country[, , "clim"])
  %>% bind_cols(df_clim_pop_ranef_cou)
  %>% mutate(
    across(
      .cols = -clim_pop, 
      .fns = ~ exp((.) + clim_pop),
      .names = "{.col}"
    )
  )
  %>% select(-clim_pop)
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    # mean_val = mean(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)

df_clim_pop_ranef_cou_summ <- (
  df_clim_pop_ranef_cou
  %>% mutate(
    clim_pop = exp(clim_pop)
  )
  %>% summarise(
    median_val = median(clim_pop),
    # mean_val = mean(clim_pop),
    lower1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)

df_clim_ranef_cou <- (
  bind_rows(
    df_clim_pop_ranef_cou_summ, 
    df_clim_gr_ranef_cou
  )
)
```

```{r}
#| fig-width: 4
#| fig-height: 3

lims <- c(
  min(df_clim_ranef_cou$lower2_val, 0.9), 
  max(df_clim_ranef_cou$upper2_val)
)

p1 <- (
  df_clim_ranef_cou
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_clim_ranef_cou
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),,
    axis.title.x = element_text(size = 14),
    axis.title.y = element_blank(),
    axis.text = element_text(size = 13),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

### Calibration Checks

```{r}
#| fig-width: 4
#| fig-height: 3
plot_calibration(fit_ranef_cou, df_model, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("calibration_plot_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

### Residuals Spatial Correlation Checks

```{r}
#| fig-width: 3.2
#| fig-height: 3
plot_moran(df_model, sf_vacs, fit = fit_ranef_cou, residuals = TRUE)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_res_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_ranef_cou, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_ranef_cou.png")
)
```

## With spatial correlations

```{r}
pars_sp <- c(
  "b_Intercept",
  "b_countryMozambique",
  "b_countryNamibia",
  "b_countryZambia",
  "b_countryZimbabwe",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  "sd_adm_name__Intercept",
  "sd_adm_name:cluster__Intercept",
  "b_clim",
  "r_country[Lesotho,clim]",
  "sdcar",
  "rcar[1]"
)
```

```{r}
stanvars <- stanvar(6, "num_pred")

prior_list_sp <- c(
  # prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(-2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  # prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1"),
  prior(beta(1, 1), class = "car"),
  # prior(beta(1, 1), class = "rhocar"),
  prior(exponential(0.5), class = "sdcar")
)

form_sp <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + clim
        # + (1 | adm_name/cluster)
        + car(W, gr = adm_name, type = 'escar')
      )"
    )
  )
)
fit_sp <- brm(
  formula = form_sp,
  family = bernoulli("logit"),
  prior = prior_list_sp,
  data = df_model,
  data2 = list(W = W_ord),
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = 4000,
  control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
sp <- rstan::get_sampler_params(fit_sp$fit, inc_warmup = FALSE)
ebfmi_per_chain <- sapply(sp, function(chain_mat) {
  ener <- chain_mat[,"energy__"]
  mean(diff(ener)^2) / var(ener)
})
print(ebfmi_per_chain)
```

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_sp), 
  pars = c(
    "b_Intercept", 
    # "sd_adm_name__Intercept",
    # "sd_adm_name:cluster__Intercept",
    # "r_country[Lesotho,clim]",
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    # "bsp_moschool_level", 
    "b_clim",
    "car",
    # "rhocar",
    "sdcar",
    "rcar[1]"
  ),
  np = nuts_params(fit_sp),
  np_style = pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
vars_to_plot <- c(
  "prior_car",
  "car",
  # "prior_rhocar",
  # "rhocar",
  "prior_sdcar",
  "sdcar"
)
plot(fit_sp, variable = vars_to_plot, regex = FALSE, nvariables = 4)
```

```{r}
bayestestR::effective_sample(fit_sp)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_sp,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_ranef_cou <- (
  fit_sp
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      contains("rcar"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_ranef_cou,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_sp <- (
  fit_sp
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_sp_stats <- (
  df_base_sv_by_country_sp
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_sp,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Climate Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(fit_sp, df_model, covs = c("clim"))
  + scale_y_continuous(
    # limits = c(0, 0.43),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_sp.png")
)
```

#### Climate Variable Posterior

```{r}
df_clim_pop_sp <- (
  fit_sp
  %>% as.data.frame()
  %>% mutate(clim_pop = exp(b_clim))
  %>% summarise(
    median_val = median(clim_pop),
    lower1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 1.2

lims <- c(
  min(df_clim_pop_sp$lower2_val, 0.95), 
  max(df_clim_pop_sp$upper2_val)
)

p1 <- (
  df_clim_pop_sp
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p1

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_", clim_label, "_", pop_label, "_", viol_label, "_sp.png")
)
```

### Calibration Checks

```{r}
#| fig-width: 4
#| fig-height: 3
plot_calibration(fit_sp, df_model, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("calibration_plot_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_sp.png")
)
```


### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_sp, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_sp.png")
)
```

## With food prices

```{r}
pars_fp <- c(
  "b_Intercept",
  "b_countryMozambique",
  "b_countryNamibia",
  "b_countryZambia",
  "b_countryZimbabwe",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  "bsp_mofood_price_above_1sd_12m1",
  "sd_adm_name__Intercept",
  "sd_adm_name:cluster__Intercept",
  "b_clim"
)
```

```{r}
stanvars <- stanvar(6, "num_pred")

prior_list_fp <- c(
  prior(student_t(3, -3, 1), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1"),
  prior(dirichlet(1), class = "simo", coef = "mofood_price_above_1sd_12m1")
)

form_fp <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + clim
        + (1 | adm_name/cluster)
        + mo(food_price_above_1sd_12m)
      )"
    )
  )
)
fit_fp <- brm(
  formula = form_fp,
  family = bernoulli("logit"),
  prior = prior_list_fp,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  # iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
sp <- rstan::get_sampler_params(fit_fp$fit, inc_warmup = FALSE)
ebfmi_per_chain <- sapply(sp, function(chain_mat) {
  ener <- chain_mat[,"energy__"]
  mean(diff(ener)^2) / var(ener)
})
print(ebfmi_per_chain)
```

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_fp), 
  pars = c(
    "b_Intercept", 
    "sd_adm_name__Intercept", 
    "sd_adm_name:cluster__Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "bsp_mofood_price_above_1sd_12m",
    "b_clim"
  ),
  np = nuts_params(fit_fp),
  np_style = pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_fp, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_fp, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_fp)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_fp,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_fp <- (
  fit_fp
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_fp,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_fp <- (
  fit_fp
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_fp_stats <- (
  df_base_sv_by_country_fp
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_fp,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_fp_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_fp_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_fp_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Climate Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(fit_fp, df_model, covs = c("clim"))
  + scale_y_continuous(
    # limits = c(0, 0.43),
    labels = scales::percent_format(accuracy = 1)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fp.png")
)
```

### Calibration Checks

```{r}
#| fig-width: 4
#| fig-height: 3
plot_calibration(fit_fp, df_model, outcome_var = viol_var)
ggsave(
  path = fig_dir,
  filename = paste0("calibration_plot_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fp.png")
)
```

### Residuals Spatial Correlation Checks

```{r}
#| fig-width: 3.2
#| fig-height: 3
plot_moran(df_model, sf_vacs, fit = fit_fp, residuals = TRUE)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_res_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fp.png")
)
```

### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_fp, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_fp.png")
)
```

## Separate observation and per-region regression

### Observation level step

```{r}
pars_obs_level <- c(
  "b_Intercept",
  "b_rural",
  "b_live_with_partner",
  "b_over_18",
  "bsp_moschool_level",
  # "sd_adm_name__Intercept",
  # "sd_adm_name:cluster__Intercept"
)
```

```{r}
stanvars <- stanvar(5, "num_pred")

prior_list_obs_level <- c(
  prior(student_t(3, -1, 0.4), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  # prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_obs_level<- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
      )"
    )
  )
)
fit_obs_level <- brm(
  formula = form_obs_level,
  family = bernoulli("logit"),
  prior = prior_list_obs_level,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

#### Summary

```{r}
bayestestR::describe_posterior(
  fit_obs_level,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Residuals

```{r}
obs_level_res <- (
  df_model
  %>% add_residual_draws(fit_obs_level)
  %>% group_by(country, adm_name)
  %>% summarise(
    clim = mean(clim, na.rm = TRUE),
    sv_np = mean(.residual, na.rm = TRUE),
    .groups = "drop"
  )
  %>% ungroup()
  %>% mutate(
    clim = scale(clim),
    sv_np = scale(sv_np)
  )
)
```

### Per-region regression

```{r}
pars_adm_reg <- c(
  "b_Intercept",
  "b_clim",
  "r_country[Lesotho,clim]"
)
```

```{r}
stanvars <- stanvar(2, "num_pred")

prior_list_reg_level <- c(
  prior(student_t(3, -1, 0.4), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b")
  # prior(exponential(1/0.2), class = "sd")
)

form_reg_level<- bf(
  as.formula(
    paste(
      viol_var,
      "~",
      "(
        1 
        + clim
      )"
    )
  )
)
fit_reg_level <- brm(
  formula = form_reg_level,
  family = gaussian(),
  prior = prior_list_reg_level,
  data = obs_level_res,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_reg_level,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_reg_level <- (
  fit_reg_level
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      contains("rcar"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_reg_level,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Climate Marginal Effects

##### Population level

```{r}
clim_center <- attr(obs_level_res[["clim"]], "scaled:center")
clim_scale <- attr(obs_level_res[["clim"]], "scaled:scale")
sv_center <- attr(obs_level_res[["sv_np"]], "scaled:center")
sv_scale <- attr(obs_level_res[["sv_np"]], "scaled:scale")
clim_marg <- (
  generate_cont_marginal_df(
    fit_reg_level,
    obs_level_res,
    covs = c("clim"),
    grid_points = 30
  )
  %>% select(-covariate)
  %>% mutate(
    across(
      -covariate_value,
      ~ ((.) * sv_scale) + sv_center
    ),
    covariate_value = (covariate_value * clim_scale) + clim_center
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 3
lims <- NULL

(
  clim_marg
  %>% ggplot(
    aes(
      x = covariate_value, 
      y = median, 
    )
  ) 
  + geom_ribbon(
    aes(ymin = lower2, ymax = upper2), 
    alpha = 0.3, 
    fill = col_palette[5],
    color = NA
  ) 
  + geom_ribbon(
    aes(ymin = lower1, ymax = upper1), 
    alpha = 0.6, 
    fill = col_palette[5],
    color = NA
  ) 
  + geom_line(
    linewidth = 1,
    color = col_palette[5]
  )
  + labs(
    y = "Marginal expected\np(violence)",
  ) 
  + scale_y_continuous(
    limits = lims,
    labels = scales::percent_format(accuracy = 1)
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_text(size = 16),
    axis.title.x = element_blank(),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15),
    legend.background = element_blank(),
    legend.title = element_blank(),
    legend.text = element_text(size = 15),
    legend.position = "inside",
    legend.position.inside = c(0.15, 0.8),
    strip.placement = "outside",
    strip.text = element_text(size = 15),
    strip.background = element_blank()
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("marginal_prob_clim_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_reg_level.png")
)
```

#### Climate Variable Posterior

```{r}
df_clim_reg_level <- (
  fit_reg_level
  %>% as.data.frame()
  %>% mutate(clim_pop = exp(b_clim))
  %>% summarise(
    median_val = median(clim_pop),
    lower1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(clim_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(clim_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 1.2

lims <- c(
  min(df_clim_reg_level$lower2_val, 0.95), 
  max(df_clim_reg_level$upper2_val)
)

p1 <- (
  df_clim_reg_level
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p1

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_", clim_label, "_", pop_label, "_", viol_label, "_reg_level.png")
)
```

### Residuals Spatial Correlation Checks

```{r}
#| fig-width: 3.2
#| fig-height: 3
plot_moran(obs_level_res, sf_vacs, fit = fit_reg_level, residuals = TRUE)
ggsave(
  path = fig_dir,
  filename = paste0("moran_plot_res_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_reg_level.png")
)
```

### Posterior Predictive Checks

```{r}
#| fig-width: 12
#| fig-height: 2.5
(
  plot_ppc_rootogram(fit_reg_level, obs_level_res, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
ggsave(
  path = fig_dir,
  filename = paste0("ppc_by_adm_main_effect_", clim_label, "_", pop_label, "_", viol_label, "_reg_level.png")
)
```

# Compare Models

```{r}
fit_fix_country <- add_criterion(
  fit_fix_country, 
  "loo",
  moment_match = TRUE
)
fit_ranint_adm_clu <- add_criterion(
  fit_ranint_adm_clu, 
  "loo",
  moment_match = TRUE
)
fit_fix_int_cc <- add_criterion(
  fit_fix_int_cc, 
  "loo",
  moment_match = TRUE
)
fit_ranef_cou <- add_criterion(
  fit_ranef_cou, 
  "loo",
  moment_match = TRUE
)
fit_sp <- add_criterion(
  fit_sp, 
  "loo",
  moment_match = TRUE
)
loo::loo_compare(
  fit_fix_country,
  fit_ranint_adm_clu,
  fit_fix_int_cc,
  fit_ranef_cou,
  fit_sp
)
```

```{r}
bind_rows(
  get_calibration_scores(fit_fix_country, df_model, outcome_var = viol_var, model_name = "Fixed country intercept"),
  get_calibration_scores(fit_ranint_adm_clu, df_model, outcome_var = viol_var, model_name = "Random intercept by region and cluster"),
  get_calibration_scores(fit_fix_int_cc, df_model, outcome_var = viol_var, model_name = "Fixed interaction, country * clim"),
  get_calibration_scores(fit_ranef_cou, df_model, outcome_var = viol_var, model_name = "Random intercept by region and cluster, random slopes by country"),
  get_calibration_scores(fit_ranef_cou, df_model, outcome_var = viol_var, model_name = "Random intercept by region and cluster, random slopes by country"),
)
```

```{r}
clim_draws_fix_country <- (
  as_draws_df(fit_fix_country)
  %>% select(clim = b_clim)
  %>% mutate(
    model = "Fixed country intercept"
  )
)

clim_draws_ranint_adm_clu <- (
  as_draws_df(fit_ranint_adm_clu)
  %>% select(clim = b_clim)
  %>% mutate(
    model = "Random intercept\nby region and cluster\n"
  )
)

clim_draws_fix_int_cc <- (
  as_draws_df(fit_fix_int_cc)
  %>% select(clim = b_clim)
  %>% mutate(
    model = "Random intercept\nby region and cluster\nfixed country * clim"
  )
)

clim_draws_ranef_cou <- (
  as_draws_df(fit_ranef_cou)
  %>% select(clim = b_clim)
  %>% mutate(
    model = "Random intercept\nby region and cluster\nrandom slopes by country"
  )
)

clim_draws <- (
  bind_rows(
    clim_draws_fix_country,
    clim_draws_ranint_adm_clu,
    clim_draws_fix_int_cc,
    clim_draws_ranef_cou
  )
  %>% mutate(
    model = factor(
      model, 
      levels = c(
        "Fixed country intercept",
        "Random intercept\nby region and cluster\n",
        "Random intercept\nby region and cluster\nfixed country * clim",
        "Random intercept\nby region and cluster\nrandom slopes by country"
      )
    )
  )
)
```

```{r}
#| fig-width: 3
#| fig-height: 7
(
  ggplot(
    data = clim_draws,
    mapping = aes(
      x = clim,
    )
  )
  + stat_dotsinterval(
    quantiles = 100,
    slab_color = col_palette[3],
    slab_fill = col_palette[4],
    .width = c(0.5, 0.95),
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + facet_wrap(
    ~model,
    ncol = 1,
    scales = "free_y",
    # strip.position = "left"
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 15),
    axis.ticks.y = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 13),
    strip.background = element_blank(),
    # strip.placement = "outside",
    strip.text = element_text(size = 13)
  )
  + labs(
    x = "Posterior Value",
    title = "Model Comparison"
  )
  + scale_y_discrete(
    expand = expansion(mult = c(0.2, 0.75))
  )
  # + scale_x_continuous(
  #   limits = c(-0.1, 1.8)
  # )
)

ggsave(
  path = fig_dir,
  filename = paste0("clim_post_comp_", clim_label, "_", pop_label, "_", viol_label, ".png")
)
```
