---
title: "Model temperature (number of excess hot days) effect on non-partner sexual violence"
project:
  output-dir: outputs
date: last-modified
format: 
  html:
    page-layout: full
toc: true
editor: visual
warning: false
execute: 
  freeze: true
  warning: false
---

# Environment Setup

```{r setup}
# Packages
library(tidyverse)
library(sf)
library(spdep)
library(brms)
options(brms.backend = "cmdstanr", mc.cores = 4)
library(posterior)
library(bayesplot)
library(tidybayes)
library(tidytext)
library(patchwork)
library(reliabilitydiag)

# Folder Structure
root <- rprojroot::has_file("extreme-heat-vs-sv.Rproj")$make_fix_file()
geo_data_dir <- root("data/raw/geographies")
proc_data_dir <- root("data/processed")
src_dir <- root("src")
fig_dir <- root("figures")
dir.create(fig_dir, showWarnings = FALSE)
```

# Notebook settings

```{r}
# Settings
nb_name <-  "Model effect of excess number of hot days on non-partner sexual violence"
seed <- sum(sapply(str_split(nb_name, pattern = "", simplify = TRUE), FUN = utf8ToInt))
set.seed(seed)

# Viz settings
col_palette <- c("#dc7726", "#eebb93", "#ecc046", "#f6e0a3", "#0292b7", "#81c9db", "#35A29F", "#97DECE")
label_map <- c(
  live_with_partner = "Live with partner (%)",
  school_level = "Education attainment (%)",
  rural = "Rural area (%)",
  over_18 = "Over 18 (%)",
  heat = "Excess hot days (std.)",
  sv = "NP-SV victimisation (%)"
)

# Var settings
heat_var <- "dev_value_temp_above_1sd_12m"
heat_label <- "excess_hot_days"
viol_var <- "sv_np"
viol_label <- "np_viol"
covars <- c(
  "sample_weight",
  "country",
  "adm_name",
  "cluster",
  "rural",
  "over_18",
  "school_level",
  "live_with_partner",
  viol_var
)
vars <- c(covars, heat_var)

# Computation settings
warmup = 500
iter = 2000
```

# Functions

```{r}
source(file.path(src_dir, "viz.R"))
source(file.path(src_dir, "model_check_utils.R"))
```

# Import Data

## Geometries

### Mozambique

```{r}
sf_moz <- (
  st_read(
    file.path(geo_data_dir, "Mozambique 2022 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Zimbabwe

```{r}
sf_zwe <- (
  st_read(
    file.path(geo_data_dir, "Zimbabwe 2015 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Lesotho

```{r}
sf_lso <- (
  st_read(
    file.path(geo_data_dir, "Lesotho 2023 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Namibia

```{r}
sf_nam <- (
  st_read(
    file.path(geo_data_dir, "Namibia 2013 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Zambia

```{r}
sf_zmb <- (
  st_read(
    file.path(geo_data_dir, "Zambia 2018 DHS - sdr_subnational_boundaries", "shps", "sdr_subnational_boundaries.shp")
  )
  %>% st_make_valid()
  %>% rename_with(tolower)
  %>% select(
    country = cntrynamee,
    adm_name = dhsregen,
    adm_code = regcode
  )
  %>% arrange(adm_code)
)
```

### Create combined shapes

```{r}
sf_all <- (
  bind_rows(
    sf_moz,
    sf_zwe,
    sf_lso,
    sf_nam,
    sf_zmb,
  )
)
```

## Heat & Violence Data

```{r}
df_heat_viol <- (
  read_csv(
    file.path(proc_data_dir, "heat_violence_final.csv"),
    show_col_type = FALSE
  )
  %>% filter(
    female == 1,
  )
  %>% mutate(
    over_18 = as.numeric(age > 18)
  )
)
```

# Stats

## All countries

```{r}
(
  df_heat_viol
  %>% summarise(
    heat = mean(!!sym(heat_var), na.rm = TRUE),
    rural = 100 * sum(rural * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    live_with_partner = 100 *sum(live_with_partner * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    over_18 = 100 * sum(over_18 * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    school_level = sum(school_level * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    sv := 100 * sum(!!sym(viol_var) * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    .groups = "drop"
  )
)
```

## Country level

```{r}
(
  df_heat_viol
  %>% group_by(country)
  %>% summarise(
    heat = mean(!!sym(heat_var), na.rm = TRUE),
    rural = 100 * sum(rural * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    live_with_partner = 100 *sum(live_with_partner * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    over_18 = 100 * sum(over_18 * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    school_level = sum(school_level * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    sv := 100 * sum(!!sym(viol_var) * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    .groups = "drop"
  )
  %>% ungroup()
)
```

## Admin level

```{r}
df_heat_viol_adm <- (
  df_heat_viol
  %>% group_by(country, adm_name)
  %>% summarise(
    heat = mean(!!sym(heat_var), na.rm = TRUE),
    rural = 100 * sum(rural * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    live_with_partner = 100 *sum(live_with_partner * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    over_18 = 100 * sum(over_18 * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    school_level = sum(school_level * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    sv := 100 * sum(!!sym(viol_var) * sample_weight, na.rm = TRUE) / sum(sample_weight, na.rm = TRUE),
    .groups = "drop"
  )
  %>% merge(
    sf_all,
    by = c("country", "adm_name"),
    all.x = TRUE
  )
  %>% st_as_sf()
)
```

# Viz

## Heat

```{r}
#| fig-width: 5
#| fig-height: 3

rng_heat <- range(df_heat_viol_adm$heat, na.rm = TRUE)

(
  df_heat_viol_adm
  %>% filter(country != "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = heat),
    color = "black",
    linewidth = 0.1
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "ggthemes::Orange-Blue Diverging",
    direction = -1,
    guide = guide_colorbar(
      label.position = "left",
      title.position = "right",
      title.vjust = 1,
      title.hjust = 0.5,
      barheight = unit(0.9, "npc")
    ),
    limits = rng_heat,
    rescaler = ~ scales::rescale_mid(., mid = 0),
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    plot.margin = margin(l = 0, r = 25),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(1.07, 0.5),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14, angle = 90),
    legend.ticks = element_line(color = "black")
  )
  + labs(
    fill = "Excess hot days (std.)"
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("map_heat_", heat_label, "_", viol_label, ".svg")
# )
```

```{r}
#| fig-width: 4
#| fig-height: 2.5

rng_heat <- range(df_heat_viol_adm$heat, na.rm = TRUE)

(
  df_heat_viol_adm
  %>% filter(country == "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = heat),
    color = "black",
    linewidth = 0.2
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "ggthemes::Orange-Blue Diverging",
    direction = -1,
    limits = rng_heat,
    rescaler = ~ scales::rescale_mid(., mid = 0),
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = NA, color = "black", linewidth = 3),
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )
  + guides(
    fill = "none"
  )
  + labs(
    fill = "Excess hot days (std.)"
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("map_heat_", heat_label, "_", viol_label, "_LSO.svg"),
#   bg = "transparent"
# )
```

## Violence

```{r}
#| fig-width: 5
#| fig-height: 3

rng_sv <- range(df_heat_viol_adm$sv, na.rm = TRUE)

(
  df_heat_viol_adm
  %>% filter(country != "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = sv),
    color = "black",
    linewidth = 0.1
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "grDevices::Rocket",
    direction = -1,
    guide = guide_colorbar(
      label.position = "left",
      title.position = "right",
      title.vjust = 1,
      title.hjust = 0.5,
      barheight = unit(0.9, "npc")
    ),
    limits = rng_sv,
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_blank(),
    plot.margin = margin(r = 25),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.background = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(1.07, 0.5),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14, angle = 90),
    legend.ticks = element_line(color = "black")
  )
  + labs(
    fill = label_map[["sv"]]
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("map_sv_", heat_label, "_", viol_label, ".svg")
# )
```

```{r}
#| fig-width: 4
#| fig-height: 2.5

rng_sv <- range(df_heat_viol_adm$sv, na.rm = TRUE)

(
  df_heat_viol_adm
  %>% filter(country == "Lesotho")
  %>% ggplot()
  + geom_sf(
    mapping = aes(fill = sv),
    color = "black",
    linewidth = 0.2
  )
  + paletteer::scale_fill_paletteer_c(
    palette = "grDevices::Rocket",
    direction = -1,
    limits = rng_sv
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = NA, color = "black", linewidth = 3),
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )
  + guides(
    fill = "none"
  )
  + labs(
    fill = label_map[["sv"]]
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("map_sv_", heat_label, "_", viol_label, "_LSO.svg"),
#   bg = "transparent"
# )
```

# Prepare Data

## Restrict locations

```{r}
sf_vacs <- (
  sf_all
  %>% filter(
    country %in% (df_heat_viol$country %>% unique()),
    adm_name %in% (df_heat_viol$adm_name %>% unique())
  )
)
```

## Extract model subset

```{r}
df_model <- (
  df_heat_viol
  %>% select(all_of(vars))
  %>% na.omit()
  %>% merge(
    sf_vacs %>% as.data.frame() %>% select(country, adm_name),
    by = c("country", "adm_name"),
    all.x = TRUE
  )
  %>% group_by(country)
  %>% mutate(
    country_sample_weight = sum(sample_weight, na.rm = TRUE),
    country_total_n = n()
  )
  %>% ungroup()
  %>% mutate(
    country = factor(country),
    adm_name = factor(adm_name),
    cluster = factor(cluster),
    school_level = factor(
      school_level,
      levels = sort(unique(school_level)),
      ordered = TRUE
    ),
    heat := scale(!!sym(heat_var)),
    sample_weight = country_total_n * sample_weight / country_sample_weight
  )
)
```

## Generate adjacency matrix

```{r}
nb_list <- poly2nb(sf_vacs)
W <- nb2mat(nb_list, style = "B", zero.policy = TRUE)
rownames(W) <- sf_vacs$adm_name
colnames(W) <- sf_vacs$adm_name
levs <- levels(df_model$adm_name)
W_ord <- W[levs, levs]
```

```{r}
edges <- (
  geostan::edges(W, unique_pairs_only = TRUE, shape = sf_vacs$geometry)
)
graph <- st_geometry(edges)
```

```{r}
plot(sf_vacs$geometry, lwd = .15)
plot(graph, add = TRUE, type = "p", col = "red")
plot(graph, add = TRUE, type = "l", col = "black")
```

# Modeling

## Random Intercepts by admin level and cluster

```{r}
set.seed(seed)
stanvars <- stanvar(6, "num_pred")

prior_list_ranint_adm_clu <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_ranint_adm_clu <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + heat
        + (1 | adm_name/cluster)
      )"
    )
  )
)
fit_ranint_adm_clu <- brm(
  formula = form_ranint_adm_clu,
  family = bernoulli("logit"),
  prior = prior_list_ranint_adm_clu,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = warmup,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_ranint_adm_clu), 
  pars = c(
    "b_Intercept", 
    "sd_adm_name__Intercept", 
    "sd_adm_name:cluster__Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_heat"
  ),
  np = nuts_params(fit_ranint_adm_clu),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_ranint_adm_clu, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_ranint_adm_clu, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_ranint_adm_clu)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_ranint_adm_clu,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_ranint_adm_clu <- (
  fit_ranint_adm_clu
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_ranint_adm_clu,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_ranint_adm_clu <- (
  fit_ranint_adm_clu
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_ranint_adm_clu_stats <- (
  df_base_sv_by_country_ranint_adm_clu
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_ranint_adm_clu,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_ranint_adm_clu_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
generate_cont_marginal_df(
  fit_ranint_adm_clu, 
  df_model, 
  covs = c("heat"), 
  ndraws = min(ndraws(fit_ranint_adm_clu), 1000)
)
```

```{r}
#| fig-width: 3.5
#| fig-height: 2.4
(
  plot_continuous_marginal(
    fit_ranint_adm_clu, 
    df_model, 
    covs = c("heat"), 
    grid_points = 20, 
    ndraws = min(ndraws(fit_ranint_adm_clu), 1000)
  )
  + labs(
    y = "NP violence (%)"
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_ranint_adm_clu.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_pop_adm_clu <- (
  fit_ranint_adm_clu
  %>% as.data.frame()
  %>% mutate(heat_pop = exp(b_heat))
  %>% summarise(
    median_val = median(heat_pop),
    lower1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 1.2

lims <- c(
  min(df_heat_pop_adm_clu$lower2_val, 0.95), 
  max(df_heat_pop_adm_clu$upper2_val)
)

p1 <- (
  df_heat_pop_adm_clu
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p1

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_adm_clu.png")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
(
  plot_calibration(fit_ranint_adm_clu, df_model, outcome_var = viol_var)
  + scale_y_continuous(
    limits = c(0, 0.6666667)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_ranint_adm_clu.svg")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram_weighted(fit_ranint_adm_clu, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_ranint_adm_clu.svg")
# )
```

## Random Intercepts by admin level and cluster + Fixed interaction

```{r}
set.seed(seed)
stanvars <- stanvar(7, "num_pred")

prior_list_fix_int_cc <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_fix_int_cc <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + (1 | adm_name/cluster)
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + country * heat
      )"
    )
  )
)
fit_fix_int_cc <- brm(
  formula = form_fix_int_cc,
  family = bernoulli("logit"),
  prior = prior_list_fix_int_cc,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = warmup,
  iter = iter,
  # control = list(adapt_delta = adapt_delta),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_fix_int_cc), 
  pars = c(
    "b_Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_heat",
    "sd_adm_name__Intercept",
    "sd_adm_name:cluster__Intercept"
  ),
  np = nuts_params(fit_fix_int_cc),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_fix_int_cc, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_fix_int_cc, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_fix_int_cc)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_fix_int_cc,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_fix_int_cc <- (
  fit_fix_int_cc
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_fix_int_cc,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_fix_int_cc <- (
  fit_fix_int_cc
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    (contains("b_country") & !contains("heat"))
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_fix_int_cc_stats <- (
  df_base_sv_by_country_fix_int_cc
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_fix_int_cc,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_fix_int_cc_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(
    fit_fix_int_cc, 
    df_model, 
    covs = c("heat"),
    ndraws = min(ndraws(fit_fix_int_cc), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_fix_int_cc.png")
# )
```

##### By Country

```{r}
#| fig-width: 12
#| fig-height: 3
(
  plot_single_continuous_marginal_by_group(
    fit_fix_int_cc, 
    df_model, 
    cov = "heat",
    ndraws = min(ndraws(fit_fix_int_cc), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_by_country_", heat_label, "_", viol_label, "_fix_int_cc.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_fix_int_cc <- (
  fit_fix_int_cc
  %>% as.data.frame()
  %>% mutate(
    `b_countryLesotho:heat` = 0
  )
  %>% select(
    heat_pop = b_heat,
    contains(":heat")
  )
  %>% mutate(
    across(
      .cols = -heat_pop, 
      .fns = ~ exp((.) + heat_pop),
      .names = "{.col}"
    ),
    heat_pop = exp(heat_pop)
  )
  %>% rename(
    Overall = heat_pop,
  )
  %>% rename_with(
    .cols = -Overall,
    .fn = ~ str_match(., "b_country(.*?):heat")[,2]
  )
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 3

lims <- c(
  min(df_heat_fix_int_cc$lower2_val, 0.9), 
  max(df_heat_fix_int_cc$upper2_val)
)

p1 <- (
  df_heat_fix_int_cc
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_heat_fix_int_cc
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),,
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 13),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_fix_int_cc.svg")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
plot_calibration(fit_fix_int_cc, df_model, outcome_var = viol_var)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_fix_int_cc.png")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram(fit_fix_int_cc, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_fix_int_cc.png")
# )
```

## Random slope by country

```{r}
set.seed(seed)
stanvars <- stanvar(6, "num_pred")

prior_list_ranef_cou <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1")
)

form_ranef_cou <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1 
        + (1 | adm_name/cluster)
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + heat
        + (-1 + heat | country)
      )"
    )
  )
)
fit_ranef_cou <- brm(
  formula = form_ranef_cou,
  family = bernoulli("logit"),
  prior = prior_list_ranef_cou,
  data = df_model,
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = warmup,
  iter = iter,
  control = list(adapt_delta = 0.95),
  # sample_prior = "only"
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_ranef_cou), 
  pars = c(
    "b_Intercept", 
    "sd_adm_name__Intercept",
    "sd_adm_name:cluster__Intercept",
    "r_country[Lesotho,heat]",
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level", 
    "b_heat"
  ),
  np = nuts_params(fit_ranef_cou),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
plot(fit_ranef_cou, variable = "prior_b", regex = TRUE, nvariables = 3)
```

```{r}
plot(fit_ranef_cou, variable = "b_rural", regex = TRUE, nvariables = 3)
```

```{r}
bayestestR::effective_sample(fit_ranef_cou)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_ranef_cou,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_ranef_cou <- (
  fit_ranef_cou
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("prior"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_ranef_cou,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_ranef_cou <- (
  fit_ranef_cou
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_ranef_cou_stats <- (
  df_base_sv_by_country_ranef_cou
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_ranef_cou,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_ranef_cou_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(
    fit_ranef_cou, 
    df_model,
    covs = c("heat"),
    ndraws = min(ndraws(fit_ranef_cou), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

##### By Country

```{r}
#| fig-width: 11
#| fig-height: 2.4
(
  plot_single_continuous_marginal_by_group(
    fit_ranef_cou,
    df_model, 
    grid_points = 15,
    ndraws = min(ndraws(fit_ranef_cou), 1000),
    cov = "heat"
  )
  + labs(
    y = "NP violence (%)"
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_by_country_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_pop_ranef_cou <- (
  fit_ranef_cou
  %>% as.data.frame()
  %>% select(heat_pop = b_heat)
)
df_heat_gr_ranef_cou <- (
  as_tibble(ranef(fit_ranef_cou, summary = FALSE)$country[, , "heat"])
  %>% bind_cols(df_heat_pop_ranef_cou)
  %>% mutate(
    across(
      .cols = -heat_pop, 
      .fns = ~ exp((.) + heat_pop),
      .names = "{.col}"
    )
  )
  %>% select(-heat_pop)
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)

df_heat_pop_ranef_cou_summ <- (
  df_heat_pop_ranef_cou
  %>% mutate(
    heat_pop = exp(heat_pop)
  )
  %>% summarise(
    median_val = median(heat_pop),
    lower1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)

df_heat_ranef_cou <- (
  bind_rows(
    df_heat_pop_ranef_cou_summ, 
    df_heat_gr_ranef_cou
  )
)
```

```{r}
#| fig-width: 4
#| fig-height: 3

lims <- c(
  min(df_heat_ranef_cou$lower2_val, 0.9), 
  max(df_heat_ranef_cou$upper2_val)
)

p1 <- (
  df_heat_ranef_cou
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_heat_ranef_cou
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 15, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),,
    axis.title.x = element_text(size = 14),
    axis.title.y = element_blank(),
    axis.text = element_text(size = 13),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
(
  plot_calibration(fit_ranef_cou, df_model, outcome_var = viol_var)
  + scale_y_continuous(
    limits = c(0, 0.6666667)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_ranef_cou.svg")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram_weighted(fit_ranef_cou, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_ranef_cou.svg")
# )
```

## With spatial correlations

```{r}
set.seed(seed)
stanvars <- stanvar(6, "num_pred")

prior_list_sp <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1"),
  prior(beta(1, 1), class = "car"),
  prior(exponential(0.5), class = "sdcar")
)

form_sp <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + heat
        + car(W, gr = adm_name, type = 'escar')
      )"
    )
  )
)
fit_sp <- brm(
  formula = form_sp,
  family = bernoulli("logit"),
  prior = prior_list_sp,
  data = df_model,
  data2 = list(W = W_ord),
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = 1000,
  iter = 3000,
  # control = list(adapt_delta = adapt_delta),
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_sp), 
  pars = c(
    "b_Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level",
    "b_heat",
    "sdcar",
    "rcar[1]"
  ),
  np = nuts_params(fit_sp),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
vars_to_plot <- c(
  "prior_car",
  "car",
  "prior_sdcar",
  "sdcar"
)
plot(fit_sp, variable = vars_to_plot, regex = FALSE, nvariables = 4)
```

```{r}
bayestestR::effective_sample(fit_sp)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_sp,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_sp <- (
  fit_sp
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("cluster"),
      contains("prior"),
      contains("rcar"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_sp,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_sp <- (
  fit_sp
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_sp_stats <- (
  df_base_sv_by_country_sp
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_sp,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_sp_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(
    fit_sp, 
    df_model, 
    covs = c("heat"),
    ndraws = min(ndraws(fit_sp), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_sp.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_pop_sp <- (
  fit_sp
  %>% as.data.frame()
  %>% mutate(heat_pop = exp(b_heat))
  %>% summarise(
    median_val = median(heat_pop),
    lower1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 1.2

lims <- c(
  min(df_heat_pop_sp$lower2_val, 0.95), 
  max(df_heat_pop_sp$upper2_val)
)

p1 <- (
  df_heat_pop_sp
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p1

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_sp.png")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
(
  plot_calibration(fit_sp, df_model, outcome_var = viol_var)
  + scale_x_continuous(
    breaks = c(0.0, 0.1, 0.2)
  )
  + scale_y_continuous(
    limits = c(0, 0.6666667)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram_weighted(fit_sp, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```

## With spatial correlations & random slopes

```{r}
set.seed(seed)
stanvars <- stanvar(6, "num_pred")

prior_list_sp_ranef <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(exponential(1/0.2), class = "sd"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1"),
  prior(beta(1, 1), class = "car"),
  prior(exponential(0.5), class = "sdcar")
)

form_sp_ranef <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1
        + country
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + heat
        + (-1 + heat | country)
        + car(W, gr = adm_name, type = 'escar')
      )"
    )
  )
)
fit_sp_ranef <- brm(
  formula = form_sp_ranef,
  family = bernoulli("logit"),
  prior = prior_list_sp_ranef,
  data = df_model,
  data2 = list(W = W_ord),
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = 1000,
  iter = 3000,
  control = list(adapt_delta = 0.95),
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_sp_ranef), 
  pars = c(
    "b_Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level",
    "b_heat",
    "r_country[Lesotho,heat]",
    "sdcar",
    "rcar[1]"
  ),
  np = nuts_params(fit_sp),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
vars_to_plot <- c(
  "prior_car",
  "car",
  "prior_sdcar",
  "sdcar"
)
plot(fit_sp_ranef, variable = vars_to_plot, regex = FALSE, nvariables = 4)
```

```{r}
bayestestR::effective_sample(fit_sp_ranef)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_sp_ranef,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_sp_ranef <- (
  fit_sp_ranef
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("cluster"),
      contains("prior"),
      contains("rcar"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_sp_ranef,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_sp_ranef <- (
  fit_sp_ranef
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    contains("b_country")
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_sp_ranef_stats <- (
  df_base_sv_by_country_sp_ranef
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_sp_ranef,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_ranef_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_ranef_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_sp_ranef_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(
    fit_sp_ranef, 
    df_model, 
    covs = c("heat"),
    ndraws = min(ndraws(fit_sp_ranef), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_sp.png")
# )
```

##### By Country

```{r}
#| fig-width: 11
#| fig-height: 2.4
(
  plot_single_continuous_marginal_by_group(
    fit_sp_ranef,
    df_model,
    grid_points = 15,
    ndraws = min(ndraws(fit_sp_ranef), 1000),
    cov = "heat"
  )
  + labs(
    y = "NP violence (%)"
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_by_country_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_pop_sp_ranef <- (
  fit_sp_ranef
  %>% as.data.frame()
  %>% select(heat_pop = b_heat)
)
df_heat_gr_sp_ranef <- (
  as_tibble(ranef(fit_sp_ranef, summary = FALSE)$country[, , "heat"])
  %>% bind_cols(df_heat_pop_sp_ranef)
  %>% mutate(
    across(
      .cols = -heat_pop, 
      .fns = ~ exp((.) + heat_pop),
      .names = "{.col}"
    )
  )
  %>% select(-heat_pop)
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)

df_heat_pop_sp_ranef_summ <- (
  df_heat_pop_sp_ranef
  %>% mutate(
    heat_pop = exp(heat_pop)
  )
  %>% summarise(
    median_val = median(heat_pop),
    lower1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(heat_pop, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(heat_pop, ci = 0.95)$CI_high,
  )
  %>% mutate(
    country = "Overall"
  )
)

df_heat_sp_ranef <- (
  bind_rows(
    df_heat_pop_sp_ranef_summ, 
    df_heat_gr_sp_ranef
  )
)
```

```{r}
#| fig-width: 4
#| fig-height: 3

lims <- c(
  min(df_heat_sp_ranef$lower2_val, 0.9), 
  max(df_heat_sp_ranef$upper2_val)
)

p1 <- (
  df_heat_sp_ranef
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_heat_sp_ranef
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 15, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),,
    axis.title.x = element_text(size = 14),
    axis.title.y = element_blank(),
    axis.text = element_text(size = 13),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
(
  plot_calibration(fit_sp_ranef, df_model, outcome_var = viol_var)
  + scale_x_continuous(
    breaks = c(0.0, 0.1, 0.2)
  )
  + scale_y_continuous(
    limits = c(0, 0.6666667)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram_weighted(fit_sp_ranef, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```

## With spatial correlations & fixed slopes

```{r}
set.seed(seed)
stanvars <- stanvar(6, "num_pred")

prior_list_sp_fixed <- c(
  prior(student_t(3, -2, 2), class = "Intercept"),
  prior(normal(0, 0.8 / sqrt(num_pred)), class = "b"),
  prior(dirichlet(1), class = "simo", coef = "moschool_level1"),
  prior(beta(1, 1), class = "car"),
  prior(exponential(0.5), class = "sdcar")
)

form_sp_fixed <- bf(
  as.formula(
    paste(
      viol_var,
      "| weights(sample_weight)",
      "~",
      "(
        1
        + rural
        + live_with_partner
        + over_18
        + mo(school_level)
        + country * heat
        + car(W, gr = adm_name, type = 'escar')
      )"
    )
  )
)
fit_sp_fixed <- brm(
  formula = form_sp_fixed,
  family = bernoulli("logit"),
  prior = prior_list_sp_fixed,
  data = df_model,
  data2 = list(W = W_ord),
  stanvars = stanvars,
  seed = seed,
  refresh = 1000,
  warmup = 1000,
  iter = 3000,
  control = list(adapt_delta = 0.95),
  sample_prior = TRUE
)
```

### Model Checks

```{r}
#| fig-width: 12
#| fig-height: 12
bayesplot::mcmc_pairs(
  as.array(fit_sp_fixed), 
  pars = c(
    "b_Intercept", 
    "b_rural",
    "b_live_with_partner",
    "b_over_18",
    "bsp_moschool_level",
    "b_heat",
    "sdcar",
    "rcar[1]"
  ),
  np = nuts_params(fit_sp_fixed),
  np_style = bayesplot::pairs_style_np(
    div_color = "green",
    div_shape = 20,
    div_size = 3
  )
)
```

```{r}
vars_to_plot <- c(
  "prior_car",
  "car",
  "prior_sdcar",
  "sdcar"
)
plot(fit_sp_fixed, variable = vars_to_plot, regex = FALSE, nvariables = 4)
```

```{r}
bayestestR::effective_sample(fit_sp_fixed)
```

### Model Output

#### Summary

##### Raw draws

```{r}
bayestestR::describe_posterior(
  fit_sp_fixed,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all",
  ci_method = "HDI"
)
```

##### Transformed draws

```{r}
trans_post_sp_fixed <- (
  fit_sp_fixed
  %>% as.data.frame()
  %>% select(
    -c(
      contains("adm_name"),
      contains("cluster"),
      contains("prior"),
      contains("rcar"),
      lprior, 
      lp__,
      Intercept
    )
  )
  %>% mutate(
    across(
      -c(contains("simo")),
      ~ exp(.)
    )
  )
)
```

```{r}
bayestestR::describe_posterior(
  trans_post_sp_fixed,
  effects = "all",
  component = "all",
  test = c(),
  centrality = "all",
  ci_method = "HDI"
)
```

#### Baseline

```{r}
df_base_sv_by_country_sp_fixed <- (
  fit_sp_fixed
  %>% as_draws_df()
  %>% select(
    b_Intercept,
    (contains("b_country") & !contains("heat"))
  )
  %>% mutate(
    b_countryLesotho = 0
  )
  %>% pivot_longer(
    cols = -b_Intercept,
    names_to = c("variable", "country"),
    names_pattern = "(b_country)(.*)",
    values_to = "b_country"
  )
  %>% mutate(
    logitp_baseline_sv = b_Intercept + b_country,
    p_baseline_sv = 1 / (1 + exp(-logitp_baseline_sv))
  )
  %>% select(country, p_baseline_sv)
)

df_base_sv_by_country_sp_fixed_stats <- (
  df_base_sv_by_country_sp_fixed
  %>% group_by(country)
  %>% summarise(
    median_p_baseline_sv = median(p_baseline_sv, na.rm = TRUE),
    mean_p_baseline_sv = mean(p_baseline_sv, na.rm = TRUE),
    lower1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_low,
    upper1_p = bayestestR::hdi(p_baseline_sv, ci = 0.5)$CI_high,
    lower2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_low,
    upper2_p = bayestestR::hdi(p_baseline_sv, ci = 0.95)$CI_high,
  )
  %>% ungroup()
)
```

```{r}
#| fig-width: 4.5
#| fig-heigh: 3
(
  ggplot(
    data = df_base_sv_by_country_sp_fixed,
    mapping = aes(
      y = fct_reorder(country, p_baseline_sv, .fun = ~ -median(.)),
      x = p_baseline_sv
    )
  )
  + ggridges::geom_density_ridges(
      aes(height = after_stat(scaled)),
      stat = "density",
      orientation = "x",
      scale = 0.6,
      rel_min_height = 0.01,
      alpha = 0.7,
      color = NA,
      fill = "#FDD0A2FF"
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_fixed_stats,
      aes(y = country, yend = country, x = lower2_p, xend = upper2_p),
      linewidth = 1,
      alpha = 0.4,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_segment(
      data = df_base_sv_by_country_sp_fixed_stats,
      aes(y = country, yend = country, x = lower1_p, xend = upper1_p),
      linewidth = 1.5,
      alpha = 0.7,
      color = "#A63603FF",
      inherit.aes = FALSE
  )
  + geom_point(
      data = df_base_sv_by_country_sp_fixed_stats,
      aes(y = country, x = median_p_baseline_sv),
      color = "#A63603FF",
      size = 3,
      inherit.aes = FALSE
  )
  + geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 13),
  )
  + labs(
      x = "Baseline Sexual Violence (%)"
  )
  + scale_y_discrete(
      expand = expansion(mult = c(0.1, 0.25))
  )
  + scale_x_continuous(
      # limits = lims,
      labels = scales::percent_format(accuracy = 1)
  )
) 
```

#### Heat Marginal Effects

##### Population level

```{r}
#| fig-width: 5
#| fig-height: 3
(
  plot_continuous_marginal(
    fit_sp_fixed, 
    df_model,
    covs = c("heat"),
    ndraws = min(ndraws(fit_sp_fixed), 1000)
  )
  + scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_", heat_label, "_", viol_label, "_sp.png")
# )
```

##### By Country

```{r}
#| fig-width: 11
#| fig-height: 2.4
(
  plot_single_continuous_marginal_by_group(
    fit_sp_fixed, 
    df_model, 
    grid_points = 15,
    ndraws = min(ndraws(fit_sp_fixed), 1000),
    cov = "heat"
  )
  + labs(
    y = "NP violence (%)"
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("marginal_prob_heat_main_effect_by_country_", heat_label, "_", viol_label, "_ranef_cou.png")
# )
```

#### Heat Variable Posterior

```{r}
df_heat_sp_fixed <- (
  fit_sp_fixed
  %>% as.data.frame()
  %>% mutate(
    `b_countryLesotho:heat` = 0
  )
  %>% select(
    heat_pop = b_heat,
    contains(":heat")
  )
  %>% mutate(
    across(
      .cols = -heat_pop, 
      .fns = ~ exp((.) + heat_pop),
      .names = "{.col}"
    ),
    heat_pop = exp(heat_pop)
  )
  %>% rename(
    Overall = heat_pop,
  )
  %>% rename_with(
    .cols = -Overall,
    .fn = ~ str_match(., "b_country(.*?):heat")[,2]
  )
  %>% pivot_longer(
    cols = everything(),
    names_to = "country",
    values_to = "value"
  )
  %>% group_by(country)
  %>% summarise(
    median_val = median(value),
    lower1_val = bayestestR::hdi(value, ci = 0.5)$CI_low,
    upper1_val = bayestestR::hdi(value, ci = 0.5)$CI_high,
    lower2_val = bayestestR::hdi(value, ci = 0.95)$CI_low,
    upper2_val = bayestestR::hdi(value, ci = 0.95)$CI_high,
    .groups = "drop"
  )
)
```

```{r}
#| fig-width: 5
#| fig-height: 3

lims <- c(
  min(df_heat_sp_fixed$lower2_val, 0.9), 
  max(df_heat_sp_fixed$upper2_val)
)

p1 <- (
  df_heat_sp_fixed
  %>% filter(country == "Overall")
  %>% ggplot(
    mapping = aes(
      y = country
    )
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[6],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      y = country,
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[5],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
      y = country,
    ),
    size = 4,
    color = col_palette[5]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),,
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

p2 <- (
  df_heat_sp_fixed
  %>% filter(country != "Overall")
  %>% ggplot(
    mapping = aes(
      y = fct_reorder(country, desc(median_val))
    )
  )
  + geom_segment(
    mapping = aes(
      x = lower2_val,
      xend = upper2_val
    ),
    color = col_palette[2],
    linewidth = 1
  )
  + geom_segment(
    mapping = aes(
      x = lower1_val,
      xend = upper1_val
    ),
    color = col_palette[1],
    linewidth = 2
  )
  + geom_point(
    mapping = aes(
      x = median_val,
    ),
    size = 4,
    color = col_palette[1]
  )
  + geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black"
  )
  + scale_x_continuous(
    limits = lims
  )
  + theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),,
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 13),
  )
  + labs(
    y = "Country",
    x = "Temperature Risk Odds Ratio"
  )
)

(
  p1 / plot_spacer() / p2
  + plot_layout(
    axes = "collect",
    heights = c(1, -0.7, 5)
  )
)

# ggsave(
#   path = fig_dir,
#   filename = paste0("heat_post_", heat_label, "_", viol_label, "_fix_int_cc.svg")
# )
```

### Calibration Checks

```{r}
#| fig-width: 3.5
#| fig-height: 3
(
  plot_calibration(fit_sp_fixed, df_model, outcome_var = viol_var)
  + scale_x_continuous(
    breaks = c(0.0, 0.1, 0.2)
  )
  + scale_y_continuous(
    limits = c(0, 0.6666667)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("calibration_plot_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```

### Posterior Predictive Checks

```{r}
#| fig-width: 9
#| fig-height: 2
(
  plot_ppc_rootogram_weighted(fit_sp_fixed, df_model, outcome_var = viol_var)
  + theme(
    legend.position = "inside",
    legend.position.inside = c(0.92, 0.8)
  )
)
# ggsave(
#   path = fig_dir,
#   filename = paste0("ppc_by_adm_main_effect_", heat_label, "_", viol_label, "_sp.svg")
# )
```
