---
title: "Preprocess Temperature  and UTCI Data"
format: html
editor: visual
---

# Environment Setup

```{r setup}
# Packages
library(tidyverse)
library(sf)
library(paletteer)

# Folder Structure
root <- rprojroot::has_file("extreme-heat-vs-sv.Rproj")$make_fix_file()
proc_data_dir <- root("data/processed")
src_dir <- root("src")
```

# Functions

```{r}
source(file.path(src_dir, "data_processing.R"))
```

# Data Import

## Temperature

```{r}
df_temp <- (
  read_csv(
    file.path(proc_data_dir, "temp_max_daily_max.csv"),
    show_col_types = FALSE
  )
)
```

## UTCI

There are 10 UTCI thermal stress categories that correspond to specific human physiological responses to the thermal environment. The categories relate to UTCI values as follows: above +46: extreme heat stress; +38 to +46: very strong heat stress; +32 to +38: strong heat stress; +26 to +32: moderate heat stress; +9 to +26: no thermal stress; +9 to 0: slight cold stress; 0 to -13: moderate cold stress; -13 to -27: strong cold stress; -27 to -40: very strong cold stress; below -40: extreme cold stress.

```{r}
df_utci <- (
  read_csv(
    file.path(proc_data_dir, "utci_max_daily.csv"),
    show_col_types = FALSE
  )
)
```

# Process Data

## Temperature

### Raw

```{r}
df_temp_12m <- calculate_temp_12m_stats(df_temp)
```

```{r}
colSums(is.na(df_temp_12m))
```

### Rolling average

```{r}
df_temp_roll_12m <- calculate_temp_12m_stats(df_temp, roll = TRUE, roll_days = 3)
```

```{r}
colSums(is.na(df_temp_roll_12m))
```

## UTCI

### Raw

```{r}
df_utci_12m <- calculate_utci_12m_stats(df_utci)
```

```{r}
colSums(is.na(df_utci_12m))
```

### Rolling average

```{r}
df_utci_roll_12m <- calculate_utci_12m_stats(df_utci, roll = TRUE, roll_days = 3)
```

```{r}
colSums(is.na(df_utci_roll_12m))
```

# Combine variables

```{r}
df_heat_12m <- ( 
  df_temp_12m
  %>% merge(
    df_temp_roll_12m,
    by = c("country", "adm_code", "adm_name", "date"),
    all.x = TRUE
  )
  %>% merge(
    df_utci_12m,
    by = c("country", "adm_code", "adm_name", "date"),
    all.x = TRUE
  )
  %>% merge(
    df_utci_roll_12m,
    by = c("country", "adm_code", "adm_name", "date"),
    all.x = TRUE
  )
)
```

# Visualizations

## Temperature

### Temperature 1sd above average

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = value_temp_above_1sd_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 30
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "# days temperature above 1 sd",
    y = "Density",
  )
)
```

### Dev temperature 1 sd above average

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = dev_value_temp_above_1sd_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 40
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "# days temperature above 1sd (dev)",
    y = "Density",
  )
)
```

### Max rolling temperature

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = value_temp_roll_max_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 30
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "Max Temperature",
    y = "Density",
  )
)
```

### Dev max rolling temperature

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = dev_value_temp_roll_max_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 40
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "Max Temperature (dev)",
    y = "Density",
  )
)
```

### Temperature 1sd above average time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    value_temp_above_1sd_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = value_temp_above_1sd_12m)
  )
  + geom_line(
    color = "#0292b7",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "# days temperature max above 1 sd (month)"
  )
)
```

### Dev temperature 1 sd above average time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    dev_value_temp_above_1sd_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = dev_value_temp_above_1sd_12m)
  )
  + geom_line(
    color = "#dc7726",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "# days temperature max above 1 sd (dev)"
  )
)
```

### Max rolling temperature time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    value_temp_roll_max_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = value_temp_roll_max_12m)
  )
  + geom_line(
    color = "#0292b7",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "Max Temperature"
  )
)
```

### Dev max rolling temperature time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    dev_value_temp_roll_max_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = dev_value_temp_roll_max_12m)
  )
  + geom_line(
    color = "#dc7726",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "Max Temperature (dev)"
  )
)
```

## UTCI

### UTCI above 32

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = value_utci_above_32_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 30
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "# days UTCI above 32",
    y = "Density",
  )
)
```

### Dev UTCI above 32

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = dev_value_temp_above_1sd_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 40
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "# days UTCI above 32 (dev)",
    y = "Density",
  )
)
```

### Max rolling UTCI

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = value_utci_roll_max_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 30
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "Max UTCI",
    y = "Density",
  )
)
```

### Dev max rolling UTCI

```{r}
(
  ggplot(
    data = df_heat_12m %>% filter(date > "2015-01-01"), 
    aes(
      x = dev_value_utci_roll_max_12m, 
      fill = country
    )
  )
  + geom_histogram(
    aes(y = after_stat(density)),
    position = "stack",
    bins = 40
  )
  + theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
      plot.background = element_blank(),
      plot.title = element_text(size = 16, hjust = 0.5),
      plot.subtitle = element_text(size = 14, hjust = 0.5),
      axis.title = element_text(size = 16),
      axis.text.y = element_text(size = 15),
      axis.text.x = element_text(size = 15),
      legend.background = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 13),
    )
  + scale_fill_paletteer_d(
    "MetBrewer::Derain",
    na.value = "transparent",
  )
  + labs(
    x = "Max UTCI (dev)",
    y = "Density",
  )
)
```

### UTCI above 32 time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    value_utci_above_32_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = value_utci_above_32_12m)
  )
  + geom_line(
    color = "#0292b7",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "# days UTCI above 32"
  )
)
```

### Dev UTCI above 32 time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    dev_value_utci_above_32_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = dev_value_utci_above_32_12m)
  )
  + geom_line(
    color = "#dc7726",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "# days UTCI above 32 (dev)"
  )
)
```

### Max rolling UTCI time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    value_utci_roll_max_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = value_utci_roll_max_12m)
  )
  + geom_line(
    color = "#0292b7",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "UTCI Max"
  )
)
```

### Dev max rolling UTCI time series

```{r}
#| fig-width: 9
#| fig-height: 5

(
  df_heat_12m
  %>% filter(
    date > "2010-01-01",
    date < "2025-01-01",
    country == "Mozambique",
    !(adm_name %in% c("Tete", "Zambezia"))
  )
  %>% select(
    date,
    adm_name,
    dev_value_utci_roll_max_12m,
  )
  %>% ggplot(
    mapping = aes(x = date, y = dev_value_utci_roll_max_12m)
  )
  + geom_line(
    color = "#dc7726",
    linewidth = 1.3
  )
  + facet_wrap(
    ~ adm_name,
    ncol = 3
  )
  + theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    panel.grid = element_blank(),
    panel.spacing.x = unit(25, "pt"),
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.background = element_blank(),
    plot.title = element_text(size = 16),
    plot.margin = margin(t = 0, r = 20, b = 0, l = 10, unit = "pt"),
    axis.ticks = element_line(linewidth = 1),
    axis.ticks.length = unit(4, "pt"),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 15),
  )
  + labs(
    x = "Date",
    y = "Max UTCI (dev)"
  )
)
```

# Save data

```{r}
df_heat_12m %>% write_csv(file.path(proc_data_dir, "processed_heat_daily_max.csv"))
```

```{r}
sessionInfo()
```
